Fitness Adventure: an interactive floor game to maintain body fitness

### 2015-02-06 paper.tex
add stuff

@@

@@

>>>>

  \section{DEVICE}
    The application runs on an $8m^2$ FTIR screen. It behaves like a multitouch screen that is capable of recognizing users via their shoe profile. We built our application on top of a framework that enables 3D elements to convey users to be part of a virtual world.

@@

\clearpage

@@

  \subsection{Do not just copy existing solution to floor apps} % (fold)
  \label{sub:do_not_just_copy_existing_solution_to_floor_apps}

    We wanted to provide a fitness application in order to perform common fitness exercises. Even in the contextual inquiry we got to know that a floor does not provide the necessary instruments to perform a rich and diverse workout. It lacks a possibility to train the shoulders for example. We tried to reduce the app to only a few possible training exercises, like push-ups, stepping and sit-ups. This would not improve the training behavior at all. We then created training exercises out of things one can do on a floor.
